---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---

Firms {data-navmenu="Firm Synthesis Model"}
============================================

Highlights {data-width=150}
--------------------------------------------

**Firm Synthesis Model: Firms in the United Stated and within the CMAP Model Region**

Firm synthesis model outputs enumerating firms by size, location, and industry.

### Synthesized Firms City of Chicago

```{r Synthesized_Firms_ValueBox_Chicago}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_CHICAGO, .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>City of Chicago</br>", icon = "fa-building-o")
```

### Synthesized Firms Cook County Outside Chicago

```{r Synthesized_Firms_ValueBox_Cook_Not_Chicago}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_COOK & !TAZ %in% BASE_TAZ_CHICAGO, .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>Cook County (Not Chicago)</br>", icon = "fa-building-o")
```

### Synthesized Firms Rest of CMAP MPO Area (Not Cook County)

```{r Synthesized_Firms_ValueBox_CMAP_MPO}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_CMAP & !TAZ %in% BASE_TAZ_COOK, .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>Rest of CMAP MPO Area (Not Cook County)</br>", icon = "fa-building-o")
```

### Synthesized Firms Rest of Region

```{r Synthesized_Firms_ValueBox_Rest_Region}
value <- format(ScenarioFirms[TAZ_TYPE == "Non-CMAP Part of Model Region", .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>Rest of Model Region</br>", icon = "fa-building-o")
```

### Synthesized Firms Model Region

```{r Synthesized_Firms_ValueBox_Model_Region}
value <- format(ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region"), .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>Model Region</br>", icon = "fa-building-o")
```

### Synthesized Firms Rest of Country

```{r Synthesized_Firms_ValueBox_Rest_USA}
value <- format(ScenarioFirms[TAZ_TYPE == "Rest of USA", .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>Rest of USA</br>", icon = "fa-building-o")
```

### Synthesized Firms USA

```{r Synthesized_Firms_ValueBox_ALL}
value <- format(ScenarioFirms[, .N], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Firms<br>All of USA</br>", icon = "fa-building-o")
```

Column {data-width=400 .tabset}
--------------------------------------------
### Firms by Industry

```{r Map_Firms_By_Industry}
k <- 25
map <- leaflet(width = "100%") %>%
  addProviderTiles(map_type, group = "Background Map")
map <- map %>% addTAZPoints(data = ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region")],
                            shp = shp,
                            group = "EmpCatGroupedName",
                            scale.factor = k) %>%
  addTAZPolygons() %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addEasyButton(easyButton(
    icon = "ion-arrow-shrink",
    title = "Reset View",
    onClick = JS("function(btn, map){
                 map.setView(map._initialCenter, map._initialZoom);}"))) %>%
  htmlwidgets::onRender(JS("function(el, x){
  var map = this;
  map.whenReady(function(){
    map._initialCenter = map.getCenter();
    map._initialZoom = map.getZoom();
  });
  }"))
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",CMAP_BBOX["ymin"],", ",CMAP_BBOX["xmin"],"),
    corner2 = new L.LatLng(",CMAP_BBOX["ymax"],", ",CMAP_BBOX["xmax"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

>`r if(SCENARIO_RUN_FIRMSYN) {paste0("Note: Each data point represents ", comma(k), " firms within model region and precise locations are illustrative as firms are only identified geographically at the TAZ-level.")}`

### Firms by Size

```{r Map_Firms_By_Size}
k <- 25
map <- leaflet(shp, width = "100%") %>%
  addProviderTiles(map_type, group = "Background Map")
map <- map %>% addTAZPoints(data = ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region")],
                            shp = shp,
                            group = "esizecat", scale.factor = k) %>%
  addTAZPolygons() %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addEasyButton(easyButton(
    icon = "ion-arrow-shrink",
    title = "Reset View",
    onClick = JS("function(btn, map){
                 map.setView(map._initialCenter, map._initialZoom);}"))) %>%
  htmlwidgets::onRender(JS("function(el, x){
  var map = this;
  map.whenReady(function(){
    map._initialCenter = map.getCenter();
    map._initialZoom = map.getZoom();
  });
  }"))
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",CMAP_BBOX["ymin"],", ",CMAP_BBOX["xmin"],"),
    corner2 = new L.LatLng(",CMAP_BBOX["ymax"],", ",CMAP_BBOX["xmax"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

>`r if(SCENARIO_DB_FIRMSYN) {paste0("Note: Each data point represents ", comma(k), " firms within model region and precise locations are illustrative as firms are only identified geographically at the TAZ-level.")}`

Column {data-width=400 .tabset}
--------------------------------------------

### Firms by Industry (CMAP Model Region)

```{r Chart_Firms_By_Industry}
# Organize
dat <- ScenarioFirms[, .N, keyby = .(Region = TAZ_TYPE, Industry = EmpCatGroupedName)]
dat[, Pct := N/sum(N), by = Region]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Industry.csv"))
assign("db_tab_firms_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Industry", yvar = "N", ylabel = "Firms",
                        fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by Industry (Rest of USA)

```{r Chart_Firms_By_Industry_RoUSA}

# Plot
bar_plotter(dat[Region == "Rest of USA"], xvar = "Industry", yvar = "N", ylabel = "Firms",
                        fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by Industry (Percent)

```{r Chart_Firms_By_Industry_Percent}

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Pct", ylabel = "Percent of Firms",
                        fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by Size (CMAP Model Region)

```{r Chart_Firms_By_Size}
# Organize
dat <- ScenarioFirms[, .N, keyby = .(Region = TAZ_TYPE, Size = esizecat)]
dat[, Pct := N/sum(N), by = Region]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Size.csv"))
assign("db_tab_firms_size", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Size", yvar = "N", xlabel = "Firm Size Category", ylabel = "Firms", fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by Size (Rest of USA)

```{r Chart_Firms_By_Size_RofUSA}

# Plot
bar_plotter(dat[Region == "Rest of USA"], xvar = "Size", yvar = "N", xlabel = "Firm Size Category", ylabel = "Firms", fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by Size (Percent)

```{r Chart_Firms_By_Size_Percent}

# Plot
bar_plotter(dat, xvar = "Size", yvar = "Pct", xlabel = "Firm Size Category", ylabel = "Percent of Firms", fill = "Region", position = "dodge", coord_flip = TRUE)
```

### Firms by District (CMAP Model Region)

```{r Chart_Firms_By_District}
# Organize
dat <- ScenarioFirms[, .N, keyby = .(Region)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_District.csv"))
assign("db_tab_firms_district", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Region", yvar = "N", xlabel = "District", ylabel = "Firms", 
             coord_flip = TRUE)
```

### Firms by Industry and Size (CMAP)

```{r Chart_Firms_By_Industry_And_Size_CMAP}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="CMAP MPO Area", .N, keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "N"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Industry_and_Size_CMAP.csv"))
assign("db_tab_firms_industry_size_cmap", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes firms within the CMAP MPO area only

### Firms by Industry and Size (Rest of Model Region)

```{r Chart_Firms_By_Industry_And_Size_Rest_Region}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="Non-CMAP Part of Model Region", .N, keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "N"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Industry_and_Size_Rest_Region.csv"))
assign("db_tab_firms_industry_size_rest_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes firms within the rest of the model region only

### Firms by Industry and Size (Rest of USA)

```{r Chart_Firms_By_Industry_And_Size_Rest_USA}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="Rest of USA", .N, keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "N"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Industry_and_Size_Rest_USA.csv"))
assign("db_tab_firms_industry_size_rest_usa", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes firms within the rest of the USA only

### Firms by Industry and District

```{r Chart_Firms_By_Industry_And_District}
# Organize
dat <- ScenarioFirms[, .N, keyby = .(Industry = EmpCatGroupedName, Region)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Region,
                     fun.aggregate = sum,
                     value.var = "N"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Firms_by_Industry_and_District.csv"))
assign("db_tab_firms_industry_district", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes firms within the \model region and in the rest of the USA

Employment {data-navmenu="Firm Synthesis Model"}
============================================

Highlights {data-width=100}
--------------------------------------------

**Firm Synthesis Model: Employment in the United Stated and within the CMAP Model Region**

Firm synthesis model outputs enumerating employment by location and industry.

### Synthesized Employment (Chicago)

```{r}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_CHICAGO, sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>City of Chicago</br>", icon = "fa-briefcase")
```

### Synthesized Firms Cook County Outside Chicago

```{r}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_COOK & !TAZ %in% BASE_TAZ_CHICAGO, sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Cook County (Not Chicago)</br>", icon = "fa-briefcase")
```

### Synthesized Employment Rest of CMAP MPO Area (Not Cook County)

```{r}
value <- format(ScenarioFirms[TAZ %in% BASE_TAZ_CMAP & !TAZ %in% BASE_TAZ_COOK, sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Rest of CMAP MPO Area (Not Cook County)</br>", icon = "fa-briefcase")
```

### Synthesized Employment (Rest of Model Region)

```{r}
value <- format(ScenarioFirms[TAZ_TYPE=="Non-CMAP Part of Model Region", sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Non-CMAP Region</br>", 
         icon = "fa-briefcase")
```

### Synthesized Employment (Model Region)

```{r}
value <- format(ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region"), sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Model Region</br>", 
         icon = "fa-briefcase")
```

### Synthesized Employment (Rest of USA)

```{r}
value <- format(ScenarioFirms[TAZ_TYPE=="Rest of USA", sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Rest of USA</br>", 
         icon = "fa-briefcase")
```

### Synthesized Employment TOTAL

```{r}
value <- format(ScenarioFirms[, sum(Employees)], big.mark = ",", trim = TRUE)
valueBox(value, caption = "Synthesized Employees<br>Total</br>", icon = "fa-briefcase")
```

Column {data-width=400 .tabset}
--------------------------------------------

### Employment by Industry

```{r Map_Employment_By_Industry}
k <- 50
map <- leaflet(shp, width = "100%") %>%
  addProviderTiles(map_type, group = "Background Map")
map <- map %>% addTAZPoints(data = ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region")],
                            shp = shp,
                            group = "EmpCatGroupedName", weight = "Employees",
                            scale.factor = k) %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addTAZPolygons()
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",CMAP_BBOX["ymin"],", ",CMAP_BBOX["xmin"],"),
    corner2 = new L.LatLng(",CMAP_BBOX["ymax"],", ",CMAP_BBOX["xmax"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

>`r if(SCENARIO_DB_FIRMSYN) {paste0("Note: Each data point represents ", comma(k), " employees and precise locations are illustrative as firms are only identified geographically at the TAZ-level.")}`

### Employment by Size

```{r Map_Employment_By_Size}
k <- 25
map <- leaflet(shp, width = "100%") %>%
  addProviderTiles(map_type, group = "Background Map")
map <- map %>% addTAZPoints(data = ScenarioFirms[TAZ_TYPE %in% c("CMAP MPO Area", "Non-CMAP Part of Model Region")],
                            shp = shp,
                            group = "esizecat", weight = "Employees",
                            scale.factor = k) %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addTAZPolygons()
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",CMAP_BBOX["ymin"],", ",CMAP_BBOX["xmin"],"),
    corner2 = new L.LatLng(",CMAP_BBOX["ymax"],", ",CMAP_BBOX["xmax"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

>`r if(SCENARIO_DB_FIRMSYN) {paste0("Note: Each data point represents ", comma(k), " employees and precise locations are illustrative as firms are only identified geographically at the TAZ-level.")}`

Column {data-width=500 .tabset}
--------------------------------------------

### Employment by Industry (CMAP Model Region)

```{r Chart_Employment_By_Industry_1}
# Organize
dat <- ScenarioFirms[, .(Employees = sum(Employees)), keyby = .(Region = TAZ_TYPE, Industry = EmpCatGroupedName)]
dat[, Pct := Employees/sum(Employees), by = Region]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Industry.csv"))
assign("db_tab_emp_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Industry", yvar = "Employees",  fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by Industry (Rest of USA)

```{r Chart_Employment_By_Industry_1_RofUSA}

# Plot
bar_plotter(dat[Region == "Rest of USA"], xvar = "Industry", yvar = "Employees",  fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by Industry (Percent)

```{r Chart_Employment_By_Industry_1_Percent}

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Pct", ylabel = "Percent of Employees",  fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by Size (CMAP Model Region)

```{r Chart_Employment_By_Size_1}
# Organize
dat <- ScenarioFirms[, .(Employees = sum(Employees)), keyby = .(Region = TAZ_TYPE, Size = esizecat)]
dat[, Pct := Employees/sum(Employees), by = Region]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Size.csv"))
assign("db_tab_emp_size", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Size", yvar = "Employees", xlabel = "Firm Size Category", 
            fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by Size (Rest of USA)

```{r Chart_Employment_By_Size_1_RofUSA}

# Plot
bar_plotter(dat[Region == "Rest of USA"], xvar = "Size", yvar = "Employees", xlabel = "Firm Size Category", 
            fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by Size (Percent)

```{r Chart_Employment_By_Size_1_Percent}

# Plot
bar_plotter(dat, xvar = "Size", yvar = "Pct", ylabel = "Percent of Employees", xlabel = "Firm Size Category", 
            fill = "Region", position = "dodge", coord_flip = TRUE)

```

### Employment by District

```{r Chart_Employment_By_District_1}
# Organize
dat <- ScenarioFirms[, .(Employees = sum(Employees)), keyby = .(Region)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_District.csv"))
assign("db_tab_emp_district", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Region != "Rest of USA"], xvar = "Region", yvar = "Employees", xlabel = "District", coord_flip = TRUE)
```

### Employment by Industry and Size (CMAP)

```{r Chart_Employment_By_Industry_And_Size_CMAP_1}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="CMAP MPO Area", .(Employees = sum(Employees)), keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "Employees"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Industry_and_Size_CMAP.csv"))
assign("db_tab_emp_industry_size_cmap", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes employment within the CMAP MPO region only

### Employment by Industry and Size (Rest of Model Region)

```{r Chart_Employment_By_Industry_And_Size_Rest_Region_1}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="Non-CMAP Part of Model Region", .(Employees = sum(Employees)), keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "Employees"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Industry_and_Size_Rest_Region.csv"))
assign("db_tab_emp_industry_size_rest_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes employment within the Rest of Model Region only

### Employment by Industry and Size (Rest of USA)

```{r Chart_Employment_By_Industry_And_Size_Rest_USA_1}
# Organize
dat <- ScenarioFirms[TAZ_TYPE=="Rest of USA", .(Employees = sum(Employees)), keyby = .(Industry = EmpCatGroupedName, Size = esizecat)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Size,
                     fun.aggregate = sum,
                     value.var = "Employees"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Industry_and_Size_Rest_USA.csv"))
assign("db_tab_emp_industry_size_rest_usa", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes employment within the Rest of USA only

### Employment by Industry and District

```{r Chart_Employment_By_Industry_And_District_1}
# Organize
dat <- ScenarioFirms[, .(Employees = sum(Employees)), keyby = .(Industry = EmpCatGroupedName, Region)]

dat <- add_totals(dcast.data.table(dat,
                     Industry ~ Region,
                     fun.aggregate = sum,
                     value.var = "Employees"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Employees_by_Industry_and_District.csv"))
assign("db_tab_emp_industry_district", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

> Includes employment within the whole model region and the rest of USA

Production {data-navmenu="Firm Synthesis Model"}
============================================

Highlights {data-width=100}
--------------------------------------------

**Firm Synthesis Model: Production by Global and United States Businesses, and those within the CMAP Model Region**

Firm synthesis model outputs simulating production of commodities by location and industry.

### Producers

```{r Number_Producers_ValueBox}
valueBox(format(firm_sim_summary$firms_sum$producers, big.mark = ","), "Number of Producers", icon = "fa-industry")
```

### Production Capacity

```{r Capacity_Producers_ValueBox}
valueBox(format(firm_sim_summary$firms_sum$producers_cap, big.mark = ",", scientific = FALSE), "Capacity at Producers (Tons/Year)", icon = "fa-balance-scale")
```

### Production Capacity (Domestic, not including Wholesalers)

```{r Capacity_Producers_Domestic_ValueBox}
valueBox(format(producers[ProdType == 1, sum(OutputCapacityTons)], big.mark = ",", scientific = FALSE), "Capacity at Domestic Producers (Tons/Year)", icon = "fa-balance-scale")
```

### Production Capacity (Foreign, producing imports)

```{r Capacity_Producers_Foreign_ValueBox}
valueBox(format(producers[ProdType == 2, sum(OutputCapacityTons)], big.mark = ",", scientific = FALSE), "Capacity at Foreign Producers (Tons/Year)", icon = "fa-balance-scale")
```

### Production Capacity (Domestic Wholesalers)

```{r Capacity_Producers_Wholesale_ValueBox}
valueBox(format(producers[ProdType == 3, sum(OutputCapacityTons)], big.mark = ",", scientific = FALSE), "Capacity at Domestic Wholesalers (Tons/Year)", icon = "fa-balance-scale")
```

Column {data-width=400 .tabset}
--------------------------------------------

###  Production by Commodity

```{r production_commodity_barcharts}

# Initial commodity table rolled up from producers and labelled
# for all of the charts and tables used in this column
# db_tab_production_commodity
# db_tab_production_commodity_dom
# db_tab_production_commodity_foreign
# db_tab_production_commodity_wholesale
# db_tab_production_commodity_region
# db_tab_consumption_commodity_census_region (4 charts - MW, NE, S, W)

producers.commodity <- merge(producers[, .(Capacity = sum(OutputCapacityTons)), 
                                       keyby = .(Commodity_SCTG, ProdType, Zone, FAFZONE)],
                             c_sctg[,.(Commodity_SCTG, 
                                       Commodity = Commodity_SCTG_desc_short,
                                       Commodity_SCTG_Group, 
                                       Commodity_Group = Commodity_SCTG_Group_label)],
                             by = "Commodity_SCTG",
                             all.x = TRUE)

producers.commodity[, Type := factor(ProdType, labels = c("Domestic", "Foreign", "Wholesale"))]
producers.commodity[TAZ_System,
    REGION := i.REGION,
    on = "FAFZONE"]
assign("db_tab_production_commodity_type_zone_fafzone", 
       producers.commodity, envir = db_inputs)

# Organize
dat <- producers.commodity[, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group, Type)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(dat[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group.csv"))
assign("db_tab_production_commodity_group", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (Domestic)

```{r production_domestic_commodity_barcharts}

# Organize
dat <- producers.commodity[ProdType == 1, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group)][order(Capacity)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group_ Domestic.csv"))
assign("db_tab_production_commodity_group_dom", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, 
            position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (Foreign)

```{r production_foreign_commodity_barcharts}

# Organize
dat <- producers.commodity[ProdType == 2, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group)][order(Capacity)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group_ Foreign.csv"))
assign("db_tab_production_commodity_group_foreign", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, 
            position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (Wholesale)

```{r production_wholesale_commodity_barcharts}

# Organize
dat <- producers.commodity[ProdType == 3, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group)][order(Capacity)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group_ Wholesale.csv"))
assign("db_tab_production_commodity_group_wholesale", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, 
            position = "stack", coord_flip = TRUE)

```

### Production by Commodity and Type (Table)

```{r production_commodity_type_table}
# Organize
dat <- producers.commodity[, .(Capacity = sum(Capacity)), 
                           keyby = .(Commodity_SCTG, Commodity, Commodity_Group, Type)]

dat <- add_totals(dcast.data.table(dat,
                     Commodity_SCTG + Commodity + Commodity_Group ~ Type,
                     fun.aggregate = sum,
                     value.var = "Capacity"),
                  idcols = 3L)

cols <- names(dat)[4:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 1, big.mark = ",", scientific = FALSE), .SDcols = cols]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Type.csv"))
assign("db_tab_production_commodity_type", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lllrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")


```

###  Production by Commodity (Chicago Region)

```{r production_commodity_region_barcharts}

# Organize
dat <- producers.commodity[Zone < 150, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group, Type)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(dat[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group_Region.csv"))
assign("db_tab_production_commodity_group_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (MidWest)

```{r production_commodity_midwest_barcharts}

# Organize
dat <- producers.commodity[, .(Capacity = sum(Capacity)), 
                           by = .(Commodity_Group, Type, REGION)]
dat.region <- dat[REGION == "MidWest"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Group_Census_Region.csv"))
assign("db_tab_production_commodity_census_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (NorthEast)

```{r production_commodity_northeast_barcharts}

# Organize
dat.region <- dat[REGION == "NorthEast"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (South)

```{r production_commodity_south_barcharts}

# Organize
dat.region <- dat[REGION == "South"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Commodity (West)

```{r production_commodity_west_barcharts}

# Organize
dat.region <- dat[REGION == "West"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Capacity = sum(Capacity)), by = Commodity_Group][order(Capacity)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

### Production by Commodity and Region (Table)

```{r production_commodity_Region_table}

# Organize
dat <- add_totals(producers.commodity[Zone < 150, .(ChicagoRegion = sum(Capacity)), 
                           keyby = .(Commodity_SCTG, Commodity, Commodity_Group)],
                  rowtotal = FALSE,
                  idcols = 3L)
dat.region <- producers.commodity[, .(Capacity = sum(Capacity)), 
                           keyby = .(Commodity_SCTG, Commodity, Commodity_Group, REGION)]
dat.region[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]
dat.region <- add_totals(dcast.data.table(dat.region,
                     Commodity_SCTG + Commodity + Commodity_Group ~ REGION,
                     fun.aggregate = sum,
                     value.var = "Capacity"),
                     idcols = 3L)
dat <- merge(dat, dat.region,
             by = c("Commodity_SCTG", "Commodity", "Commodity_Group"),
             all = TRUE, sort = FALSE)

cols <- names(dat)[4:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 1, big.mark = ",", scientific = FALSE), .SDcols = cols]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Commodity_Region_Table.csv"))
assign("db_tab_production_commodity_region_census_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lllrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> NOTE: The MidWest Census Region includes the Chicago Region

Column {data-width=400 .tabset}
--------------------------------------------

###  Production by Industry

```{r production_industry_barcharts}

# Initial industry table rolled up from producers and labelled
# for all of the charts and tables used in this column

producers.industry <- producers[, .(Capacity = sum(OutputCapacityTons)), 
                                       keyby = .(EmpCatName, ProdType, Zone, FAFZONE)]

producers.industry[c_n2_empcats,
    Industry := i.EmpCatLabel,
    on = "EmpCatName"]
producers.industry[, Type := factor(ProdType, labels = c("Domestic", "Foreign", "Wholesale"))]
producers.industry[TAZ_System,
    REGION := i.REGION,
    on = "FAFZONE"]
assign("db_tab_production_industry_type_zone_fafzone", 
       producers.industry, envir = db_inputs)

# Organize
dat <- producers.industry[, .(Capacity = sum(Capacity)),
                          by = .(Industry, Type)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Capacity = sum(Capacity)), by = Industry][order(Capacity)]$Industry))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Industry.csv"))
assign("db_tab_production_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Industry (Chicago Region)

```{r production_industry_region_barcharts}

# Organize
dat <- producers.industry[Zone < 150, .(Capacity = sum(Capacity)),
                          by = .(Industry, Type)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Capacity = sum(Capacity)), by = Industry][order(Capacity)]$Industry))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Industry_Region.csv"))
assign("db_tab_production_industry_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Capacity", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Production by Industry (Census Region)

```{r production_industry_census_barcharts}

# Organize
dat <- producers.industry[, .(Capacity = sum(Capacity)),
                          by = .(Industry, Type, REGION)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Capacity = sum(Capacity)), by = Industry][order(Capacity)]$Industry))]
dat[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Industry_Census_Region.csv"))
assign("db_tab_production_industry_census_region", dat, envir = db_inputs)

# Plot
p <- ggplot(data = dat, aes(Industry, Capacity, fill = Type)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual("Type", values = rgb(rsgcolordf[c(2, 3, 4),],maxColorValue = 255), labels = c("Domestic", "Foreign", "Wholesale")) +
  xlab("Industry") +
  scale_y_continuous(name = "Capacity") +
  theme(axis.ticks = element_blank(), legend.position="bottom") +
  facet_wrap(~REGION, ncol = 2) +
  coord_flip()
p

```

### Production by Industry and Region (Table)

```{r production_Industry_Region_table}

# Organize
dat <- add_totals(producers.industry[Zone < 150, .(ChicagoRegion = sum(Capacity)),
                          by = .(Industry)],
                  rowtotal = FALSE)
dat.region <- producers.industry[, .(Capacity = sum(Capacity)), 
                           keyby = .(Industry, REGION)]
dat.region[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]
dat.region <- add_totals(dcast.data.table(dat.region,
                     Industry ~ REGION,
                     fun.aggregate = sum,
                     value.var = "Capacity"))
dat <- merge(dat, dat.region,
             by = c("Industry"),
             all = TRUE, sort = FALSE)

cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 1, big.mark = ",", scientific = FALSE), .SDcols = cols]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_by_Industry_Region_Table.csv"))
assign("db_tab_production_industry_region_census_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lrrrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> NOTE: The MidWest Census Region includes the Chicago Region

Consumption {data-navmenu="Firm Synthesis Model"}
============================================

Highlights {data-width=100}
--------------------------------------------

**Firm Synthesis Model: Consumption by Global and United States Businesses, and those within the CMAP Model Region**

Firm synthesis model outputs simulating consumption of commodities by location and industry.

### Consumers

```{r Number_Consumers_ValueBox}
valueBox(format(firm_sim_summary$firms_sum$consumers, big.mark = ","), "Number of Consumers", icon = "fa-industry")
```

### Consumption Requirements

```{r Requirements_Consumers_ValueBox}
valueBox(format(sum(firm_sim_summary$consumers_summary$Requirements), big.mark = ",", scientific = FALSE), "Requirements of Consumers (Tons/Year)", icon = "fa-balance-scale")
```

### Consumption Requirements (Domestic, not including Wholesalers)

```{r Requirements_Consumers_Domestic_ValueBox}
valueBox(format(firm_sim_summary$consumers_summary[ConsType == 1, sum(Requirements)], big.mark = ",", scientific = FALSE), "Requirements at Domestic Consumers (Tons/Year)", icon = "fa-balance-scale")
```

### Consumption Requirements (Foreign, consuming exports)

```{r Requirements_Consumers_Foreign_ValueBox}
valueBox(format(firm_sim_summary$consumers_summary[ConsType == 2, sum(Requirements)], big.mark = ",", scientific = FALSE), "Requirements at Foreign Consumers (Tons/Year)", icon = "fa-balance-scale")
```

### Consumption Requirements (Simulated in PMG)

```{r Requirements_Consumers_Simulated_PMG_ValueBox}
valueBox(format(firm_sim_summary$consumers_summary[ConsSegment == "Simulated in PMG", sum(Requirements)], big.mark = ",", scientific = FALSE), "Requirements Simulated in PMG (Tons/Year)", icon = "fa-balance-scale")
```

### Consumption Requirements (Non-Simulated Consumption)

```{r Requirements_Consumers_Non_Simulated_ValueBox}
valueBox(format(firm_sim_summary$consumers_summary[ConsSegment == "Non-Simulated Consumption", sum(Requirements)], big.mark = ",", scientific = FALSE), "Non-Simulated Consumption Requirements (Tons/Year)", icon = "fa-balance-scale")
```

Column {data-width=400 .tabset}
--------------------------------------------

###  Consumption by Commodity

```{r consumption_commodity_barcharts}

# Initial commodity table rolled up from producers and labelled
# for all of the charts and tables used in this column

consumers.commodity <- merge(firm_sim_summary$consumers_summary[, .(Requirements = sum(Requirements)), 
                                       keyby = .(Commodity_SCTG, ConsType, Zone, FAFZONE)],
                             c_sctg[,.(Commodity_SCTG, 
                                       Commodity = Commodity_SCTG_desc_short,
                                       Commodity_SCTG_Group, 
                                       Commodity_Group = Commodity_SCTG_Group_label)],
                             by = "Commodity_SCTG",
                             all.x = TRUE)

consumers.commodity[, Type := factor(ConsType, labels = c("Domestic", "Foreign"))]
consumers.commodity[TAZ_System,
    REGION := i.REGION,
    on = "FAFZONE"]
assign("db_tab_consumption_commodity_type_zone_fafzone", 
       consumers.commodity, envir = db_inputs)

# Organize
dat <- consumers.commodity[, .(Requirements = sum(Requirements)), 
                           by = .(Commodity_Group, Type)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(dat[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Group.csv"))
assign("db_tab_consumption_commodity_group", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (Domestic)

```{r consumption_domestic_commodity_barcharts}

# Organize
dat <- consumers.commodity[ConsType == 1, .(Requirements = sum(Requirements)), 
                           by = .(Commodity_Group)][order(Requirements)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Group_Domestic.csv"))
assign("db_tab_consumption_commodity_group_domestic", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (Foreign)

```{r consumption_foreign_commodity_barcharts}

# Organize
dat <- consumers.commodity[ConsType == 2, .(Requirements = sum(Requirements)), 
                           by = .(Commodity_Group)][order(Requirements)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Group_Foreign.csv"))
assign("db_tab_consumption_commodity_group_foreign", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (Chicago Region)

```{r consumption_commodity_region_barcharts}

# Organize
dat <- consumers.commodity[Zone < 150, .(Requirements = sum(Requirements)), 
                           by = .(Commodity_Group, Type)]
dat[, Commodity_Group := factor(Commodity_Group, levels = unique(dat[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Group_Region.csv"))
assign("db_tab_consumption_commodity_group_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (MidWest)

```{r consumption_commodity_midwest_barcharts}

# Organize
dat <- consumers.commodity[, .(Requirements = sum(Requirements)), 
                           by = .(Commodity_Group, Type, REGION)]
dat.region <- dat[REGION == "MidWest"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Group_Census_Region.csv"))
assign("db_tab_consumption_commodity_Group_census_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (NorthEast)

```{r consumption_commodity_northeast_barcharts}

# Organize
dat.region <- dat[REGION == "NorthEast"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Commodity (South)

```{r consumption_commodity_south_barcharts}

# Organize
dat.region <- dat[REGION == "South"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)


```

###  Consumption by Commodity (West)

```{r consumption_commodity_west_barcharts}

# Organize
dat.region <- dat[REGION == "West"]
dat.region[, Commodity_Group := factor(Commodity_Group, levels = unique(dat.region[, .(Requirements = sum(Requirements)), by = Commodity_Group][order(Requirements)]$Commodity_Group))]

# Plot
bar_plotter(dat.region, xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

### Consumption by Commodity and Region (Table)

```{r consumption_commodity_Region_table}

# Organize
dat <- add_totals(consumers.commodity[Zone < 150, .(ChicagoRegion = sum(Requirements)), 
                           keyby = .(Commodity_SCTG, Commodity, Commodity_Group)],
                  rowtotal = FALSE,
                  idcols = 3L)
dat.region <- consumers.commodity[, .(Requirements = sum(Requirements)), 
                           keyby = .(Commodity_SCTG, Commodity, Commodity_Group, REGION)]
dat.region[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]
dat.region <- add_totals(dcast.data.table(dat.region,
                     Commodity_SCTG + Commodity + Commodity_Group ~ REGION,
                     fun.aggregate = sum,
                     value.var = "Requirements"),
                     idcols = 3L)
dat <- merge(dat, dat.region,
             by = c("Commodity_SCTG", "Commodity", "Commodity_Group"),
             all = TRUE, sort = FALSE)

cols <- names(dat)[4:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 1, big.mark = ",", scientific = FALSE), .SDcols = cols]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Commodity_Region_Table.csv"))
assign("db_tab_consumption_commodity_region_census_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lllrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> NOTE: The MidWest Census Region includes the Chicago Region

### Comparison of Production and Consumption by Commodity

```{r production_consumption_commodity_barcharts}

# Organize
dat.cons <- consumers.commodity[, .(Annual_Quantity = sum(Requirements)), 
                           by = .(Commodity_Group)][, Type := "Consumption"]
dat.prod <- producers.commodity[, .(Annual_Quantity = sum(Capacity)), 
                           by = .(Commodity_Group)][, Type := "Production"]
dat <- rbind(dat.cons, dat.prod)

dat[, Commodity_Group := factor(Commodity_Group, levels = unique(dat[, .(Annual_Quantity = sum(Annual_Quantity)), by = Commodity_Group][order(Annual_Quantity)]$Commodity_Group))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_Consumption_by_Commodity_Group.csv"))
assign("db_tab_production_consumption_commodity_group", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Commodity_Group", yvar = "Annual_Quantity", xrotate = TRUE, fill = "Type", position = "dodge", coord_flip = TRUE)

```

Column {data-width=400 .tabset}
--------------------------------------------

###  Consumption by Industry

```{r consumption_industry_barcharts}

# Initial industry table rolled up from consumers and labelled
# for all of the charts and tables used in this column

consumers.industry <- firm_sim_summary$consumers_summary[, .(Requirements = sum(Requirements)), 
                                       keyby = .(EmpCatName, ConsType, Zone, FAFZONE)]
consumers.industry[c_n2_empcats,
    Industry := i.EmpCatLabel,
    on = "EmpCatName"]
consumers.industry[, Type := factor(ConsType, labels = c("Domestic", "Foreign"))]
consumers.industry[TAZ_System,
    REGION := i.REGION,
    on = "FAFZONE"]
assign("db_tab_consumption_industry_type_zone_fafzone", 
       producers.industry, envir = db_inputs)

# Organize
dat <- consumers.industry[, .(Requirements = sum(Requirements)),
                 keyby = .(Industry, Type)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Requirements = sum(Requirements)), by = Industry][order(Requirements)]$Industry))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Industry.csv"))
assign("db_tab_consumption_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Industry (Chicago Region)

```{r consumption_industry_region_barcharts}

# Organize
dat <- consumers.industry[Zone < 150, .(Requirements = sum(Requirements)),
                 keyby = .(Industry, Type)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Requirements = sum(Requirements)), by = Industry][order(Requirements)]$Industry))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Industry_Region.csv"))
assign("db_tab_consumption_industry_region", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Requirements", xrotate = TRUE, fill = "Type", position = "stack", coord_flip = TRUE)

```

###  Consumption by Industry (Census Region)

```{r consumption_industry_census_barcharts, fig.height=10}

# Organize
dat <- consumers.industry[, .(Requirements = sum(Requirements)),
                          by = .(Industry, Type, REGION)]
dat[, Industry := factor(Industry, levels = unique(dat[, .(Requirements = sum(Requirements)), by = Industry][order(Requirements)]$Industry))]
dat[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Industry_Census_Region.csv"))
assign("db_tab_consumption_industry_census_region", dat, envir = db_inputs)

# Plot
p <- ggplot(data = dat, aes(Industry, Requirements, fill = Type)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual("Type", values = rgb(rsgcolordf[c(2, 3, 4),],maxColorValue = 255), labels = c("Domestic", "Foreign")) +
  xlab("Industry") +
  scale_y_continuous(name = "Requirements") +
  theme(axis.ticks = element_blank(), legend.position="bottom") +
  facet_wrap(~REGION, ncol = 2) +
  coord_flip()
p

```

### Consumption by Industry and Region (Table)

```{r consumption_Industry_Region_table}

# Organize
dat <- add_totals(consumers.industry[Zone < 150, .(ChicagoRegion = sum(Requirements)),
                          by = .(Industry)],
                  rowtotal = FALSE)
dat.region <- consumers.industry[, .(Requirements = sum(Requirements)), 
                           keyby = .(Industry, REGION)]
dat.region[, REGION := factor(REGION, levels = c("MidWest","NorthEast","South","West","Foreign"))]
dat.region <- add_totals(dcast.data.table(dat.region,
                     Industry ~ REGION,
                     fun.aggregate = sum,
                     value.var = "Requirements"))
dat <- merge(dat, dat.region,
             by = c("Industry"),
             all = TRUE, sort = FALSE)

cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 1, big.mark = ",", scientific = FALSE), .SDcols = cols]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Consumption_by_Industry_Region_Table.csv"))
assign("db_tab_consumption_industry_region_census_region", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lrrrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> NOTE: The MidWest Census Region includes the Chicago Region

### Comparison of Production and Consumption by Industry

```{r production_consumption_industry_barcharts}

# Organize
dat.cons <- consumers.industry[, .(Annual_Quantity = sum(Requirements)), 
                           by = .(Industry)][, Type := "Consumption"]
dat.prod <- producers.industry[, .(Annual_Quantity = sum(Capacity)), 
                           by = .(Industry)][, Type := "Production"]
dat <- rbind(dat.cons, dat.prod)

dat[, Industry := factor(Industry, levels = unique(dat[, .(Annual_Quantity = sum(Annual_Quantity)), by = Industry][order(Annual_Quantity)]$Industry))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Production_Consumption_by_Industry.csv"))
assign("db_tab_production_consumption_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Annual_Quantity", xrotate = TRUE, fill = "Type", position = "dodge", position.dodge = TRUE, coord_flip = TRUE)

```

<!-- ```{r section_build_firm_sim_cal, results='asis', eval=SCENARIO_DB_CALIBRATION} -->
<!-- section_firm_sim_cal <- knitr::knit_child('section_firm_sim_cal.Rmd', -->
<!--                               envir = environment(), -->
<!--                               quiet = TRUE) -->
<!-- cat(unlist(section_firm_sim_cal), sep = '\n') -->
<!-- ``` -->

```{r section_build_firm_sim_ref, results='asis', eval=SCENARIO_DB_REFERENCE}
section_firm_sim_ref <- knitr::knit_child('section_firm_sim_ref.Rmd',
                              envir = environment(),
                              quiet = TRUE)
cat(unlist(section_firm_sim_ref), sep = '\n')
```