---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---

Compare Firms Emp {data-navmenu="Firm Synthesis Model"}
=======================================================

firm_sim_taz_land_use {data-width=400 .tabset}
--------------------------------------------

**Firm Synthesis Model: Comparisons with Reference Scenario**

Firm synthesis output comparisons with reference scenario outputs:

- firm_sim_taz_land_use processes land use inputs and prepares a database for use in later steps of the model. 
- firm_sim_scale_employees scales the synthesized establishment list to match TAZ employment totals by industry.

Scenarios being compared:

- the current scenario is **`r SCENARIO_NAME`**
- the reference scenario is **`r SCENARIO_REFERENCE_NAME`**

### firm_sim_taz_land_use: Employment by Industry in Chicago Region

```{r Chart_firm_sim_taz_land_use_industry}

# Organize
# Current scenario
dat_scen <- melt.data.table(TAZLandUseCVTM, id.vars = c("TAZ", "Mesozone", "CountyFIPS"), variable.name = "Industry", value.name = "Employment")[!Industry %in% c("HH", "NEmp_Total")]
dat_scen[, Industry := sub("NEmp_", "", Industry)]
dat_scen <- dat_scen[, .(Employment = sum(Employment), Source = SCENARIO_NAME), keyby = Industry] 

# Reference scenario
dat_ref <- melt.data.table(ref_TAZLandUseCVTM, id.vars = c("TAZ", "Mesozone", "CountyFIPS"), variable.name = "Industry", value.name = "Employment")[!Industry %in% c("HH", "NEmp_Total")]
dat_ref[, Industry := sub("NEmp_", "", Industry)]
dat_ref <- dat_ref[, .(Employment = sum(Employment), Source = SCENARIO_REFERENCE_NAME), keyby = Industry] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_taz_land_use_industry_scen_compare.csv"))
assign("db_tab_firm_sim_taz_land_use_industry_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Employment",  fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_taz_land_use_industry_scen_compare.png")

```

### firm_sim_taz_land_use: Employment by District in Chicago Region

```{r Chart_firm_sim_taz_land_use_emp_District}

# Organize
# Current scenario
dat_scen <- melt.data.table(TAZLandUseCVTM, id.vars = c("TAZ", "Mesozone", "CountyFIPS"), variable.name = "Industry", value.name = "Employment")[Industry %in% c("HH", "NEmp_Total")]
dat_scen[, Industry := sub("NEmp_", "", Industry)]
dat_scen[TAZ_System, District := i.DistrictName, on = "TAZ"]
dat_scen[, TAZ_TYPE := ifelse(TAZ %in% BASE_TAZ_CMAP, "CMAP MPO Area", "Rest of Model Region")]
dat_scen <- dat_scen[, .(Employment = sum(Employment), Source = SCENARIO_NAME), keyby = .(Industry, District)] 

# Reference scenario
dat_ref <- melt.data.table(ref_TAZLandUseCVTM, id.vars = c("TAZ", "Mesozone", "CountyFIPS"), variable.name = "Industry", value.name = "Employment")[Industry %in% c("HH", "NEmp_Total")]
dat_ref[, Industry := sub("NEmp_", "", Industry)]
dat_ref[TAZ_System, District := i.DistrictName, on = "TAZ"]
dat_ref[, TAZ_TYPE := ifelse(TAZ %in% BASE_TAZ_CMAP, "CMAP MPO Area", "Rest of Model Region")]
dat_ref <- dat_ref[, .(Employment = sum(Employment), Source = SCENARIO_REFERENCE_NAME), keyby = .(Industry, District)] 

# Combine
dat <- rbind(dat_scen[Industry == "Total"], dat_ref[Industry == "Total"])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[, District := factor(District, levels = levels(TAZ_System$DistrictName))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_taz_land_use_emp_district_scen_compare.csv"))
assign("db_tab_firm_sim_taz_land_use_emp_district_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "District", yvar = "Employment", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_taz_land_use_emp_district_scen_compare.png")

```

### firm_sim_taz_land_use: Households by District in Chicago Region

```{r Chart_firm_sim_taz_land_use_hh_district}
# Organize
# Combine
dat <- rbind(dat_scen[Industry == "HH"], dat_ref[Industry == "HH"])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
setnames(dat, c("Industry", "Employment"), c("Landuse", "Households"))
dat[, District := factor(District, levels = levels(TAZ_System$DistrictName))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_taz_land_use_hh_district_scen_compare.csv"))
assign("db_tab_firm_sim_taz_land_use_hh_district_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "District", yvar = "Households", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_taz_land_use_hh_district_scen_compare.png")

```

firm_sim_scale_employees {data-width=400 .tabset}
--------------------------------------------

### firm_sim_scale_employees: Employment by Industry Groups

```{r Chart_firm_sim_scale_employees_industry}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_NAME), keyby = .(Industry = EmpCatGroupedName)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_REFERENCE_NAME), keyby = .(Industry = EmpCatGroupedName)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_industry_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_industry_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Employment", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_industry_scen_compare.png")

```

### firm_sim_scale_employees: Employment by Industry (Detailed)

```{r Chart_firm_sim_scale_employees_industry_detailed}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_NAME), keyby = .(EmpCatName)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_REFERENCE_NAME), keyby = .(EmpCatName)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[c_n2_empcats,
    Industry := i.EmpCatLabel,
    on = "EmpCatName"]
dat[, Industry := factor(Industry, levels = c_n2_empcats$EmpCatLabel)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_industry_detailed_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_industry_detailed_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Employment", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_industry_detailed_scen_compare.png")

```

### firm_sim_scale_employees: Employment by District in Chicago Region

```{r Chart_firm_sim_scale_employees_District}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[Region != "Rest of USA", .(Employment = sum(Employees), Source = SCENARIO_NAME), keyby = .(District = Region)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[Region != "Rest of USA", .(Employment = sum(Employees), Source = SCENARIO_REFERENCE_NAME), keyby = .(District = Region)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[, District := factor(District, levels = levels(TAZ_System$DistrictName))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_district_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_district_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "District", yvar = "Employment", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_district_scen_compare.png")

```

### firm_sim_scale_employees: Employment by Census Region

```{r Chart_firm_sim_scale_employees_census_region}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_NAME), keyby = .(FAFZONE)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[, .(Employment = sum(Employees), Source = SCENARIO_REFERENCE_NAME), keyby = .(FAFZONE)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[TAZ_System,
    REGION := i.REGION,
    on = "FAFZONE"]
dat <- dat[, .(Employment = sum(Employment)), keyby = .(Source, Census_Region = REGION)] 

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_census_region_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_census_region_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Census_Region", yvar = "Employment", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_census_region_scen_compare.png")

```

### firm_sim_scale_employees: Establishments by Industry (Detailed)

```{r Chart_firm_sim_scale_employees_est_industry_detailed}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[, .(Establishments = .N, Source = SCENARIO_NAME), keyby = .(EmpCatName)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[, .(Establishments = .N, Source = SCENARIO_REFERENCE_NAME), keyby = .(EmpCatName)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[c_n2_empcats,
    Industry := i.EmpCatLabel,
    on = "EmpCatName"]
dat[, Industry := factor(Industry, levels = c_n2_empcats$EmpCatLabel)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_establishments_industry_detailed_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_establishments_industry_detailed_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Establishments", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_establishments_industry_detailed_scen_compare.png")

```

### firm_sim_scale_employees: Firm Size by Industry (Detailed)

```{r Chart_firm_sim_scale_employees_firmsize_industry_detailed}
# Organize
# Current scenario
dat_scen <- ScenarioFirms[, .(Employment = sum(Employees), Establishments = .N, Source = SCENARIO_NAME), keyby = .(EmpCatName)] 

# Reference scenario
dat_ref <- ref_ScenarioFirms[, .(Employment = sum(Employees), Establishments = .N, Source = SCENARIO_REFERENCE_NAME), keyby = .(EmpCatName)] 

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[c_n2_empcats,
    Industry := i.EmpCatLabel,
    on = "EmpCatName"]
dat[, Industry := factor(Industry, levels = c_n2_empcats$EmpCatLabel)]
dat[, Firm_Size := Employment/Establishments]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_scale_employees_firm_size_industry_detailed_scen_compare.csv"))
assign("db_tab_firm_sim_scale_employees_firm_size_industry_detailed_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Firm_Size", fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_scale_employees_firm_size_industry_detailed_scen_compare.png")

```

Compare Prod Cons {data-navmenu="Firm Synthesis Model"}
=======================================================

production {data-width=400 .tabset}
--------------------------------------------

**Firm Synthesis Model: Comparisons with Reference Scenario**

Firm synthesis output comparisons with reference scenario outputs:

- production of commodities by location and industry.
- consumption of commodities by location and industry.

Scenarios being compared:

- the current scenario is **`r SCENARIO_NAME`**
- the reference scenario is **`r SCENARIO_REFERENCE_NAME`**


### Production by Commodity Group (Total)

```{r Chart_firm_sim_production_commodity}

# Organize
# Current scenario
# (use the tabulation produced earlier in the dashboard, saved in db_inputs)
dat_scen <- db_inputs$db_tab_production_commodity_group
dat_scen[, Source := SCENARIO_NAME]
  
# Reference scenario
dat_ref <- ref_db_tab_production_commodity_group
dat_ref[, Source := SCENARIO_REFERENCE_NAME]

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_production_commodity_group_scen_compare.csv"))
assign("db_tab_firm_sim_production_commodity_group_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat[,.(Capacity = sum(Capacity)), by = .(Commodity_Group, Source)], xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_production_total_commodity_group_scen_compare.png")

```

### Production by Commodity Group (Domestic, Non-Wholesale)

```{r Chart_firm_sim_production_commodity_domestic}

# Plot
bar_plotter(dat[Type == "Domestic"], xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_production_domestic_commodity_group_scen_compare.png")

```

### Production by Commodity Group (Foreign)

```{r Chart_firm_sim_production_commodity_foreign}

# Plot
bar_plotter(dat[Type == "Foreign"], xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_production_foreign_commodity_group_scen_compare.png")

```

### Production by Commodity Group (Wholesale)

```{r Chart_firm_sim_production_commodity_wholesale}

# Plot
bar_plotter(dat[Type == "Wholesale"], xvar = "Commodity_Group", yvar = "Capacity", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_production_wholesale_commodity_group_scen_compare.png")

```

### Production by Commodity Group (Table)

### Production by Commodity (Table)

```{r Table_firm_sim_production_commodity}

# Organize
# Current scenario
# (use the tabulation produced earlier in the dashboard, saved in db_inputs)
dat_scen <- db_inputs$db_tab_production_commodity_type
setnames(dat_scen, names(dat_scen)[4:ncol(dat_scen)], paste(SCENARIO_NAME, names(dat_scen)[4:ncol(dat_scen)], sep = "_"))

# Reference scenario
dat_ref <- ref_db_tab_production_commodity_type
setnames(dat_ref, names(dat_ref)[4:ncol(dat_ref)], paste(SCENARIO_REFERENCE_NAME, names(dat_ref)[4:ncol(dat_ref)], sep = "_"))

# Combine
dat <- merge(dat_ref, dat_scen, 
             by = c("Commodity_SCTG", "Commodity", "Commodity_Group"),
             sort = FALSE)

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_production_commodity_type_scen_compare.csv"))
assign("db_tab_firm_sim_production_commodity_type_scen_compare", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE,align = "lllrrrrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(c(7, 11), background = "#f2f2f2")


```

consumption {data-width=400 .tabset}
--------------------------------------------

### Consumption by Commodity Group (Total)

```{r Chart_firm_sim_consumption_commodity}

# Organize
# Current scenario
# (use the tabulation produced earlier in the dashboard, saved in db_inputs)
dat_scen <- db_inputs$db_tab_consumption_commodity_group
dat_scen[, Source := SCENARIO_NAME]
  
# Reference scenario
dat_ref <- ref_db_tab_consumption_commodity_group
dat_ref[, Source := SCENARIO_REFERENCE_NAME]

# Combine
dat <- rbind(dat_scen, dat_ref)
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_consumption_commodity_group_scen_compare.csv"))
assign("db_tab_firm_sim_consumption_commodity_group_scen_compare", dat, envir = db_inputs)

# Plot
bar_plotter(dat[,.(Requirements = sum(Requirements)), by = .(Commodity_Group, Source)], xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_consumption_total_commodity_group_scen_compare.png")

```

### Consumption by Commodity Group (Domestic)

```{r Chart_firm_sim_consumption_commodity_domestic}

# Plot
bar_plotter(dat[Type == "Domestic"], xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_consumption_domestic_commodity_group_scen_compare.png")

```

### Consumption by Commodity Group (Foreign)

```{r Chart_firm_sim_consumptioncommodity_foreign}

# Plot
bar_plotter(dat[Type == "Foreign"], xvar = "Commodity_Group", yvar = "Requirements", xrotate = TRUE, fill = "Source", position = "dodge", coord_flip = TRUE, png_name = "p_firm_sim_consumption_foreign_commodity_group_scen_compare.png")

```

### Consumption by Commodity Group (Table)

### Consumption by Commodity (Table)

<!-- ```{r Table_firm_sim_consumption_commodity} -->

<!-- # Organize -->
<!-- # Current scenario -->
<!-- # (use the tabulation produced earlier in the dashboard, saved in db_inputs) -->
<!-- dat_scen <- db_inputs$db_tab_consumption_commodity_type -->
<!-- setnames(dat_scen, names(dat_scen)[4:ncol(dat_scen)], paste(SCENARIO_NAME, names(dat_scen)[4:ncol(dat_scen)], sep = "_")) -->

<!-- # Reference scenario -->
<!-- dat_ref <- ref_db_tab_production_commodity_type -->
<!-- setnames(dat_ref, names(dat_ref)[4:ncol(dat_ref)], paste(SCENARIO_REFERENCE_NAME, names(dat_ref)[4:ncol(dat_ref)], sep = "_")) -->

<!-- # Combine -->
<!-- dat <- merge(dat_ref, dat_scen,  -->
<!--              by = c("Commodity_SCTG", "Commodity", "Commodity_Group"), -->
<!--              sort = FALSE) -->

<!-- # Save -->
<!-- fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "firm_sim_production_commodity_type_scen_compare.csv")) -->
<!-- assign("db_tab_firm_sim_production_commodity_type_scen_compare", dat, envir = db_inputs) -->

<!-- # Table -->
<!-- kable(dat, escape=FALSE,align = "lllrrrrrrrr") %>% -->
<!--   kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>% -->
<!--   row_spec(nrow(dat), background = "#f2f2f2") %>% -->
<!--   column_spec(c(7, 11), background = "#f2f2f2") -->


<!-- ``` -->

